### 2019-03-19 5_evaluation.tex
More work on evaluation.

@@

\input{e3_metg_compute}

\subsection{Number of Dependencies}

@@

>>>>

% Really want this to appear in the next section, but Latex forces it to be placed here to get the layout we want.
\input{e3_metg_compute}

@@

METG is a useful metric in part because it summarizes the basic task
scheduling overhead of a system in a single number. This makes it
possible to evaluate METG at different node counts to see how it is
impacted by changes in communication topology and latency.

Figure~\ref{fig:metg-compute} shows how METG(50\%) varies with node
count for a variety of dependence patterns supported by Task Bench:

\begin{itemize}
\item Figure~\ref{fig:metg-compute-stencil} is a 1D stencil where each
  task depends on 3 other tasks (including the same point in the
  previous timestep).
\item Figure~\ref{fig:metg-compute-nearest} is a pattern where each
  task depends on its 5 nearest neighbors.
\item Figure~\ref{fig:metg-compute-spread} is a pattern where each
  task depends on 5 distant neighbors, spread as widely as possible
  throughout the machine.
\item Figure~\ref{fig:metg-compute-4x-nearest} shows 4 simultaneous
  copies of the nearest dependence pattern.
\end{itemize}

In general, the least complicated pattern (stencil) is most favorable
to MPI, as it represents a truly bulk synchronous task graph with no
opportunity for task parallelism. For the stencil pattern, the
dominating factor is the basic overhead of executing a task, which is
minimal for MPI as the Task Bench implementation is bulk synchronous
and simply executes tasks one after another in alternation with
communication phases. In contrast the asynchronous execution
mechanisms of the other systems is pure overhead in this scenario.

The gap between MPI and other systems shrinks as the complexity of the
communication pattern grows, can even reverse as task parallelism is
added in the form of multiple task graphs.

% FIXME: update this when we have more data

Most systems for high-performance computing are horizontally scalable,
but this is not true of all the systems included in this
evaluation. Lower is better in Figure~\ref{fig:metg-compute}, and a
flat line is ideal. Systems with non-scalable implementations shows
lines that go up with node count. Most notably, Spark is typically
intended for use in industrial data center applications with task
granularities measured in tens of seconds. Spark uses a centralized
controller which limits throughput, and this is visible in the figure
as line for Spark immediately rises with node count. Keep in mind also
that Spark is being evaluated here with a non-trivial dependence
pattern which is relatively unrepresentative of Spark's normal use
cases. Spark is more efficient with trivial parallelism, as described
in Section~\ref{subsec:number-of-dependencies}.

% FIXME: talk about starpu and parsec?

\subsection{Number of Dependencies}
\label{subsec:number-of-dependencies}

@@

\subsection{Comparison with Published Results}
